SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-01-22 paper_rl/paper.tex
Small fix

\cite{campos_skip_2018} develop a technique that includes a \textit{skip gate} into LSTM or GRU \todo{citation needed} cells. It works without \gls{rl} but on the downside, their method cannot only be trained once and not be adapted afterwards and also it explicitly depends on the the implementation of the underlying classifier.

>>>>

\cite{campos_skip_2018} develop a technique that includes a \textit{skip gate} into LSTM or GRU \todo{citation needed} cells. It works without \gls{rl} but on the downside, their method can only be trained once and not be adapted afterwards and also it explicitly depends on the the implementation of the underlying classifier, while we want to be independent of it.
